### 2012-05-26 trunk/GUIErrorDetector/paper/evaluation.tex
make the wording more precisely
address issues besides orphans and widows

The subjects used in our experiment (Table~\ref{table:subjects})
include end-user applications, programming tools, and games.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.6\tabcolsep}
\begin{tabular}{|p{4.4cm}||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods \\
\hline \hline
\multicolumn{4}{|l|}{SWT desktop applications}   \\
 %\hline
 %VirgoFTP (1.3.5) &  10815 &  116 &  1955\\
 \hline
 FileBunker (1.1.2)&  14237 &  150 &  1106  \\
 \hline
 ArecaBackup (7.2)&   23226 &  444 &  4729 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner (1.0.0) &  3101 &  48 &  354\\
 \hline
 HudsonEclipse(1.0.9)&  11077 &  74 &  649 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox (1.7) &  2353 &  42  &  224 \\
 \hline
 SudokuSolver (1.06)&  3555 &  10 &  62 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
 \hline
 Fennec (d7fa4814218d)&  8577 &  51 &  620 \\
 \hline
 MyTracks (01d5c1e1cd47)&  20297 &  143 &  1374 \\
\hline
\hline
 Total &  \totaloc &  978 &  9266 \\
\hline
\multicolumn{4}{l}{}   \\
\hline
 GUI framework (version) & LOC & Classes & Methods  \\
\hline \hline
 SWT (3.6)&  129942 &  999 &  9643 \\
\hline
 Eclipse plugin development (3.6.2)&  460830 &  6630 &  37183 \\
\hline
Swing (1.6)&  167961 &  878 &  13159 \\
\hline
 Android (3.2)&  683289 &  5085 &  10584 \\
\hline
\hline
 Total &  1442022 &  13592 &  70569\\
\hline
\end{tabular}

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open-source programs
used in our evaluation. Column ``LOC'' is the number of lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its GUI framework, as listed in
the bottom table.}} 
\end{table}

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.14\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & Requiring Wrappers  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c||}{RTA }& \multicolumn{3}{|c||}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
\cline{2-11}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning \\
\hline \hline
\multicolumn{11}{|l|}{SWT desktop applications}   \\
 %\hline
 %VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
 \hline
 ArecaBackup&  20882 &  1  &  0 & 19697 & 1 & 1  & 116398 & 1 & 1 & 3021\\
 \hline
 \hline
\multicolumn{11}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202  \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 \\
 \hline
 \hline
\multicolumn{11}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210  \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356  \\
 \hline
 \hline
\multicolumn{11}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  1 / 16 &  0 / 0 & 9546 / 9682& 0 / 4& 0 / 1 & 35198 / 35756 & 0 / 1  & 0 / 1& 104 \\
 \hline
 Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 \\
\hline
\hline
 Total & 186760 / 187323&  176 / 250 & 4 / 4 & 138583 / 142196& 132 / 136& 5 / 6 & 534223 / 609158& 19 / 20 & 8 / 10 & 6393\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding invalid-thread-access errors
in multithreaded GUI programs. Column ``CG Size'' is the number of nodes in the
call graph. Column ``\#Warning''
is the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Column groups ``RTA'', ``0-CFA'',
and ``1-CFA'' show the results of using different
call graph construction algorithms.
For the Android applications, a slash ``/'' separates the result of
using standard call graph construction algorithm and our call
graph construction algorithm in Section~\ref{sec:cgcon} (dealing
with reflection calls and adding \annotationnum native method annotations
for SGTPuzzler). The \newbugs errors found in FileBunker, ArecaBackup,
S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
results of the ``Requiring Wrappers'' approach (Section~\ref{sec:straightforward}),
are shown at the far right.} }
\end{table*}

@@

%Table~\ref{table:results} show the errors in
%our subject programs, and Table~\ref{table:filters} show
%the effect of applying each heuristic filter.
\smallstep

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

@@

\enlargethispage{5pt}

@@

This approach identifies every
error that our technique found.
However, requiring wrappers 
issues a huge number of warnings,
most of which are probably false positives (see the far right column of
Table~\ref{table:results}).
The primary reason is that this simple approach
does not globally reason about the calling relationship between
threads, UI-accessing methods, and safe UI methods, and thus it often incorrectly
classifies GUI accessing operations which will never be executed
in a non-UI thread as erroneous. Furthermore, our technique
outputs a method call chain with each reported error, which can help
developers understand how an invalid thread access error is triggered.

@@

We next compare the 3 call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph:  they
mix calls to the same method from different callers into a single node, thus
introducing imprecision. Although the error paths exist in
the less precise graphs, our algorithm does not report them because of its heuristics
for outputting the shortest possible call chain. Figure~\ref{fig:ex} illustrates this point.

@@

The results in Table~\ref{table:results} also show that using the
call graph construction algorithm in Section~\ref{sec:cgcon}
helps in finding errors in Android applications. One error from the MyTracks Android application
can only be found by using the reflection-aware call graph construction algorithm (Section~\ref{sec:cg}).
This is because the error-related GUI object (\CodeIn{msgTextView}) in MyTracks is created
reflectively as follows.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
We ran this variant on each subject program for 1 hour.  It explored 5.1$\times$$10^9$ paths
on average, but did not output any of the 10 errors before it terminated.
The number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible to enumerate all paths for a realistic call graph.
In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
of each node is 2.15.  The number of distinct
non-cyclic paths is astronomically large; a rough estimate is
$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.34\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 & \multicolumn{6}{|c|}{Number of Warnings}  \\
\cline{2-7}
 Subject & Before & \multicolumn{2}{|c|}{Sound Filters}  &  \multicolumn{3}{|c|}{Heuristic Filters}  \\
\cline{3-7}
 Program &Filtering  & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 %\hline
 %VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
 \hline
 FileBunker &  4494 &  4494 &  4494 &  3210 &  10  & 2\\
 \hline
 ArecaBackup &  6219 &  438 & 438 &  438  &  1 & 1\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1644 &  1644 &  1644 & 1644 &  6 & 6\\
 \hline
 HundsonEclipse&  1367 &  567 &  567 & 567 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  31978 & 30975 &  9 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 58  &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  122 &  84 & 80 & 80 &  9 & 3\\
 \hline
 MyTracks &  1176 &  1176 &  483 & 441 &  69 & 1 \\
\hline
 \hline
 Total &  60610 &  40440 &  39753 &  37414 &  110 & \warnings \\
 \hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
sound and heuristic error filters. Column ``Before Filtering''
shows the number of warnings by the reflection-aware 1-CFA algorithm.
Other algorithms show similar patterns, which are omitted for brevity.
Column ``$F_{i,...,j}$'' represents the number of remaining warnings after applying
the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
The numbers in the last column are the same as the subcolumn ``\#Warning"
under column ``1-CFA'' in Table~\ref{table:results}.
} } \vspace{-2mm}
\end{table}

@@

Table~\ref{table:filters} measures the effectiveness of the
error filters of Section~\ref{sec:heuristic}.
The five error filters removed 99.96\% of the reported warnings as likely false positives
or redundant warnings. Specifically, the two sound filters 1 and 2 
removed 34.44\% of the warnings, and the three heuristic filters 3, 4, and 5
removed a further 65.52\% of the warnings. The most effective filter is
\#4, for removing reports with the same head methods from the entry node to \CodeIn{Thread.start()}.

>>>>

The subjects used in our experiment (Figure~\ref{table:subjects})
include end-user applications, programming tools, and games.

@@

\begin{figure}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.6\tabcolsep}
\begin{tabular}{|p{4.4cm}||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods \\
\hline \hline
\multicolumn{4}{|l|}{SWT desktop applications}   \\
 %\hline
 %VirgoFTP (1.3.5) &  10815 &  116 &  1955\\
 \hline
 FileBunker (1.1.2)&  14237 &  150 &  1106  \\
 \hline
 ArecaBackup (7.2)&   23226 &  444 &  4729 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner (1.0.0) &  3101 &  48 &  354\\
 \hline
 HudsonEclipse(1.0.9)&  11077 &  74 &  649 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox (1.7) &  2353 &  42  &  224 \\
 \hline
 SudokuSolver (1.06)&  3555 &  10 &  62 \\
 \hline
 \hline
\multicolumn{4}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
 \hline
 Fennec (d7fa4814218d)&  8577 &  51 &  620 \\
 \hline
 MyTracks (01d5c1e1cd47)&  20297 &  143 &  1374 \\
\hline
\hline
 Total &  \totaloc &  978 &  9266 \\
\hline
\multicolumn{4}{l}{}   \\
\hline
 GUI framework (version) & LOC & Classes & Methods  \\
\hline \hline
 SWT (3.6)&  129942 &  999 &  9643 \\
\hline
 Eclipse plugin development (3.6.2)&  460830 &  6630 &  37183 \\
\hline
Swing (1.6)&  167961 &  878 &  13159 \\
\hline
 Android (3.2)&  683289 &  5085 &  10584 \\
\hline
\hline
 Total &  1442022 &  13592 &  70569\\
\hline
\end{tabular}

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open-source programs
used in our evaluation. Column ``LOC'' is the number of lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its GUI framework, as listed in
the bottom table.}} 
\end{figure}

@@

\begin{figure*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.14\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & Requiring Wrappers  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c||}{RTA }& \multicolumn{3}{|c||}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
\cline{2-11}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning \\
\hline \hline
\multicolumn{11}{|l|}{SWT desktop applications}   \\
 %\hline
 %VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
 \hline
 ArecaBackup&  20882 &  1  &  0 & 19697 & 1 & 1  & 116398 & 1 & 1 & 3021\\
 \hline
 \hline
\multicolumn{11}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202  \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 \\
 \hline
 \hline
\multicolumn{11}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210  \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356  \\
 \hline
 \hline
\multicolumn{11}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  1 / 16 &  0 / 0 & 9546 / 9682& 0 / 4& 0 / 1 & 35198 / 35756 & 0 / 1  & 0 / 1& 104 \\
 \hline
 Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 \\
\hline
\hline
 Total & 186760 / 187323&  176 / 250 & 4 / 4 & 138583 / 142196& 132 / 136& 5 / 6 & 534223 / 609158& 19 / 20 & 8 / 10 & 6393\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding invalid-thread-access errors
in multithreaded GUI programs. Column ``CG Size'' is the number of nodes in the
call graph. Column ``\#Warning''
is the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Column groups ``RTA'', ``0-CFA'',
and ``1-CFA'' show the results of using different
call graph construction algorithms.
For the Android applications, a slash ``/'' separates the result of
using standard call graph construction algorithm and our call
graph construction algorithm in Section~\ref{sec:cgcon} (dealing
with reflection calls and adding \annotationnum native method annotations
for SGTPuzzler). The \newbugs errors found in FileBunker, ArecaBackup,
S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
results of the ``Requiring Wrappers'' approach (Section~\ref{sec:straightforward}),
are shown at the far right.} }
\end{figure*}

@@

\smallstep

@@

As shown in Figure~\ref{table:results}, our tool found
errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

@@

@@

This approach identifies every
error that our technique found.
However, requiring wrappers 
issues a huge number of warnings,
most of which are probably false positives (see the far right column of
Figure~\ref{table:results}).
The primary reason is that this simple approach
does not globally reason about the calling relationship between
threads, UI-accessing methods, and safe UI methods, and thus it often incorrectly
classifies GUI accessing operations which will never be executed
in a non-UI thread as erroneous. Furthermore, our technique
outputs a method call chain with each reported error, which can help
developers understand how an invalid thread access error is triggered.

@@

We next compare the 3 call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Figure~\ref{table:results},  1-CFA found
more errors than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph:  they
mix calls to the same method from different callers into a single node, thus
introducing imprecision. Although the error paths exist in
the less precise graphs, our algorithm does not report them because of its heuristics
for outputting the shortest possible call chain. Figure~\ref{fig:ex} illustrates this point.

@@

The results in Figure~\ref{table:results} also show that using the
call graph construction algorithm in Section~\ref{sec:cgcon}
helps in finding errors in Android applications. One error from the MyTracks Android application
can only be found by using the reflection-aware call graph construction algorithm (Section~\ref{sec:cg}).
This is because the error-related GUI object (\CodeIn{msgTextView}) in MyTracks is created
reflectively as follows.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
We ran this variant on each subject program for 1 hour.  It explored 5.1$\times$$10^9$ paths
on average, but did not output any potential errors before it terminated.
The number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible to enumerate all paths for a realistic call graph.
In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
of each node is 2.15.  The number of distinct
non-cyclic paths is astronomically large; a rough estimate is
$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.

@@

\begin{figure}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.34\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 & \multicolumn{6}{|c|}{Number of Warnings}  \\
\cline{2-7}
 Subject & Before & \multicolumn{2}{|c|}{Sound Filters}  &  \multicolumn{3}{|c|}{Heuristic Filters}  \\
\cline{3-7}
 Program &Filtering  & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 %\hline
 %VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
 \hline
 FileBunker &  4494 &  4494 &  4494 &  3210 &  10  & 2\\
 \hline
 ArecaBackup &  6219 &  438 & 438 &  438  &  1 & 1\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1644 &  1644 &  1644 & 1644 &  6 & 6\\
 \hline
 HundsonEclipse&  1367 &  567 &  567 & 567 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  31978 & 30975 &  9 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 58  &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  122 &  84 & 80 & 80 &  9 & 3\\
 \hline
 MyTracks &  1176 &  1176 &  483 & 441 &  69 & 1 \\
\hline
 \hline
 Total &  60610 &  40440 &  39753 &  37414 &  110 & \warnings \\
 \hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
sound and heuristic error filters. Column ``Before Filtering''
shows the number of warnings by the reflection-aware 1-CFA algorithm.
Other algorithms show similar patterns, which are omitted for brevity.
Column ``$F_{i,...,j}$'' represents the number of remaining warnings after applying
the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
The numbers in the last column are the same as the subcolumn ``\#Warning"
under column ``1-CFA'' in Figure~\ref{table:results}.
} } \vspace{-2mm}
\end{figure}

@@

Figure~\ref{table:filters} measures the effectiveness of the
error filters of Section~\ref{sec:heuristic}.
The five error filters removed 99.96\% of the reported warnings as likely false positives
or redundant warnings. Specifically, the two sound filters 1 and 2 
removed 34.44\% of the warnings, and the three heuristic filters 3, 4, and 5
removed a further 65.52\% of the warnings. The most effective filter is
\#4, for removing reports with the same head methods from the entry node to \CodeIn{Thread.start()}.
